\LARGE \bf {\sc underworlds}: Cascading Situation Assessment for Robots

### 2018-07-13 paper.tex
Final changes, taking into account the reviewer's comments

\uwds is fundamentally about distributing two datastructures: a scene graph
(with nodes representing spatial entities) and a timeline (where events are
stored as a flat list). Typical time and space complexities arise from these
datastructures. In typical usage scenarios (where the number of nodes or events
remain relatively small), the computational load to manipulate these
datastructures is however dominated by the actual processings performed by the
clients with the data.

@@

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{tools}
    \caption{Screenshot of the network topology introspection tool. Worlds are represented as boxes; clients as ellipses.}
    \label{fig|explorer}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{laasudws}
    \caption{Schema of the \uwds architecture used in the MuMMER project.
    Clients (blue boxes) read and generate the worlds whose names are in typewriter
    fonts. The last two worlds, {\tt HUMAN\{1,2\}\_PERSPECTIVE}, do not only
    represent the immediate visual perspective of the two humans, but integrate
    as well their past visual perceptions. As such, they are the \emph{visual
    memories} of the humans, that the robot can rely on when making decisions.}
    \label{fig|mummerarchitecture}
\end{figure}
%The interaction scenario requires a number of \uwds clients. The clients are
%distributed across...

>>>>

\uwds is fundamentally about distributing two datastructures: a scene graph
(with nodes representing spatial entities) and a timeline (where events are
stored as a flat list). Typical time and space complexities arise from these
datastructures. In typical usage scenarios (where the number of nodes or events
remain under a few hundred relatively small), the computational load to manipulate these
datastructures is however dominated by the actual processings performed by the
clients with the data. In the current implementation, scene graphs and timelines
are stored in-memory. Were they required, serialization and persistent storage
are not anticipated to be difficult to implement.

@@

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{tools}
    \caption{Screenshot of the network topology introspection tool, with
    arbitrary examples of worlds (represented as boxes) and clients (ellipses).
    CLients are connected to the worlds either as
    \emph{readers} or \emph{providers} of data. \uwds introspection features
    make it possible to also visualise when clients were last active.}
    \label{fig|explorer}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{laasudws}
    \caption{Schema of the \uwds architecture used in the MuMMER project.
    Clients read and generate the worlds {\tt ENV} $\rightarrow$ {\tt
    ENV\_ROBOT} $\rightarrow$ \ldots $\rightarrow$ {\tt
    HUMAN*\_PERSPECTIVE}. The last two worlds {\tt HUMAN\{1,2\}\_PERSPECTIVE}
    represent the immediate visual perspective of each of the humans, as well as
    their past visual perceptions. As such, they are the \emph{visual
    memories} of the humans, that the robot can rely on when making decisions.}
    \label{fig|mummerarchitecture}
\end{figure}
%The interaction scenario requires a number of \uwds clients. The clients are
%distributed across...
